### 2021-10-19 paper/paper.tex
in the introduction, clarified that I assume you're doing software engineering for testability and that I don't want to talk about that here

\vskip 6pt
The first unit tests for a new library often derive from mimicking how a user might write client code. These happy-path tests are narrative. We may add tests for corner cases of a function under test, but these are limited by imagination and available effort.

\vskip 6pt
Automated testing tools aid that effort. Some measure the quality of existing tests. Others select which tests to run depending on test coverage or recent code modifications. Let's focus on the first antidote to the biases inherent in narrative testing, automated generation of test cases.

>>>>

\vskip 6pt
The first unit tests for a new library often derive from mimicking how a user might write client code. These happy-path tests are narrative because they tell stories of successful use. As we develop, we strengthen tests where we see risk in code. For low-level code, this may mean testing corner cases. For high-level code, it may mean modifying the code to be easier to test~\cite{chowdhary2009practicing}. Once we've done this software engineering, we can ask what tools within our testing framework can help improve test quality.

\vskip 6pt
Some automated testing tools measure the quality of existing tests. Others select which tests to run depending on test coverage or recent code modifications. Let's focus on the first antidote to the biases inherent in narrative testing, automated generation of test cases.
